Notes of Quantum Field Theory in a Nutshell

### 2016-08-16 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Daily update. New resource for QFT.

% TODO why not odd terms
Then he notes about the Landau-Ginzburg view:

@@

Then, it discuss a process, very similar to the idea in linear
response theory in condensed matter physics. The idea is to
set up a source and a sink in which particles are created and
annihilated. It correspondes to adding a term $sum_a J_a(t)q_a$ to
the potential, or in the continuum limit, a term $\int d^DxJ(x)\phi(x)$.

@@

Here he centers at the the Lagrangian
\begin{align}
    \mathcal{L}(\phi)=\frac{1}{2}\left( (\partial\phi)^2-m^2\phi^2\right)
\end{align}
The corresponding theory is called the \textbf{free} or 
\textbf{Guassian theory}. Using 
% TODO why is it called free
\ref{eq:QFT_in_a_Nutshell_Part_I.3.classicalFieldEq}, one can easily
obtain the Klein-Gorden equation:
\begin{align}
    (\partial^2+m^2)\phi=0
\end{align}
The plain wave solution is of the form:
\begin{align}
    \omega^2=\vec{k}^2+m^2
\end{align}
He notes that by transfer back to the SI unit, one will
recognize above equations the same as the $E=mc^2$ identity.

@@

\section{I.5 Coulomb an Newton: Repulsion and Attraction}
This section tries to replicate the previous section's procedure to
produce a repulsive force. It starts with the Maxwell's Lagrangian for
electromagnetism $\mathcal{L}=-\frac{1}{4} F_{\mu\nu}F^{\mu\nu}$.
However, the authors adds an additional mass term and let the mass
$m\to 0$ in the end. This is declared to be avoiding the complication of
gauge invariance. The result is surprisingly simple. We have:
\begin{align}
    D_{\nu\lambda}(k)&=\frac{-g_{\nu\lambda}+k_\nu k_\lambda/m^2}
        {k^2-m^2}
    \nonumber\\
    W(J)&=\frac{1}{2} \int \frac{d^4k}{(2\pi)^4}
        J^\mu (k)^* \frac{1}{k^2-m^2+i\epsilon} J_\mu(k)
    \nonumber\\
    E&=\frac{1}{4\pi r}e^{-mr} 
\end{align}

This clearly represent the idea of repulsive Coulomb force.
\chapter{Bibliography}
\begin{thebibliography}{1}
	\bibitem{zee} A. Zee. Quantum Field Theory in a Nutshell
		2ed. PUP.
\end{thebibliography}
\chapter{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
	Commons Attribution-NonCommercial-ShareAlike 4.0 International 
	License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

>>>>

Then he notes about the Landau-Ginzburg view:

@@

Then, it discuss a process, very similar to the idea in linear
response theory in condensed matter physics. The idea is to
set up a source and a sink in which particles are created and
annihilated. It correspondes to adding a term $\sum_a J_a(t)q_a$ to
the potential, or in the continuum limit, a term $\int d^DxJ(x)\phi(x)$.

@@

Here he centers at the the Lagrangian
\begin{align}
    \mathcal{L}(\phi)=\frac{1}{2}\left( (\partial\phi)^2-m^2\phi^2\right)
\end{align}
The corresponding theory is called the \textbf{free} or 
\textbf{Guassian theory}. Using 
\ref{eq:QFT_in_a_Nutshell_Part_I.3.classicalFieldEq}, one can easily
obtain the Klein-Gorden equation:
\begin{align}
    (\partial^2+m^2)\phi=0
\end{align}
The plain wave solution is of the form:
\begin{align}
    \omega^2=\vec{k}^2+m^2
\end{align}
He notes that by transfer back to the SI unit, one will
recognize above equations the same as the $E=mc^2$ identity.

@@

\section{I.5 Coulomb an Newton: Repulsion and Attraction}
\paragraph{Why like charges repel}

This section tries to replicate the previous section's procedure to
produce a repulsive force. It starts with the Maxwell's Lagrangian for
electromagnetism $\mathcal{L}=-\frac{1}{4} F_{\mu\nu}F^{\mu\nu}$.
However, the authors adds an additional mass term and let the mass
$m\to 0$ in the end. This is declared to be avoiding the complication of
gauge invariance. The result is surprisingly simple. We have:
\begin{align}
    D_{\nu\lambda}(k)&=\frac{-g_{\nu\lambda}+k_\nu k_\lambda/m^2}
        {k^2-m^2}
    \nonumber\\
    W(J)&=\frac{1}{2} \int \frac{d^4k}{(2\pi)^4}
        J^\mu (k)^* \frac{1}{k^2-m^2+i\epsilon} J_\mu(k)
    \nonumber\\
    E&=\frac{1}{4\pi r}e^{-mr} 
\end{align}

This clearly represent the idea of repulsive Coulomb force.

\paragraph{Bypassing Maxwell}
% TODO stopped here.
I am not sure what to write here, since I lost grip of which field
the author is trying to calculate: meson of spin 1? or phonton?.
\chapter{Bibliography}
\begin{thebibliography}{1}
	\bibitem{zee} A. Zee. Quantum Field Theory in a Nutshell
		2ed. PUP.
\end{thebibliography}
\chapter{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
	Commons Attribution-NonCommercial-ShareAlike 4.0 International 
	License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
